Factors Influencing Early Childhood Comprehension of American English

### 2024-11-26 paper/paper.qmd
update paper

\newpage
## Predictor variables
There are eight predictor variables for my study after cleaning. @tbl-Predictor shows the descriptions of each predictor variable.

```{r}
#| label: tbl-Predictor
#| fig-cap: "Descriptions of Each Predictor Variable"
#| echo: false
#| warning: false

@@

\newpage
# Model

@@

# Results

@@

# Appendix {-}

# Additional data details

>>>>

\newpage
## Predictor variables
There are eight predictor variables for my study after cleaning. The Descriptions of Each Predictor Variable is in @tbl-Predictor shows at [Appendix -@sec-data-details].

@@

\newpage
# Model{#sec-model}

@@

# Results{#sec-result}

@@

# Appendix {-}
# Additional data details {#sec-data-details}
```{r}
#| label: tbl-Predictor
#| fig-cap: "Descriptions of Each Predictor Variable"
#| echo: false
#| warning: false
